Mamary Gland Development Exploratory Data Analysis

### 2017-02-28 src/QCAnalysis.Rmd
added tSNE based on cc-annotated genes

```
***
## Save Data
```{r}
pD.add <- select(pD.filtered, barcode, sf, tSNE1, tSNE2)
fD.add <- select(fD.filtered, id, highVar)
pD <- left_join(pD,pD.add, by="barcode")
fD <- left_join(fD,fD.add, by="id")
stopifnot(identical(as.character(pD$barcode),colnames(m)))
stopifnot(identical(as.character(fD$id),rownames(m)))
out <- list()
out[[1]] <- m
out[[2]] <- pD
out[[3]] <- fD
saveRDS(out,file="../data/Robjects/ExpressionList_QC.rds")
```

>>>>

#tsnePlot based on cell Cycle
library(scLVM)
ens_ids_cc <- getEnsembl('GO:0007049')
sel <- rownames(m.norm) %in% ens_ids_cc
fPCA <- log2(t(m.norm[sel,])+1)
fPCA <- scale(fPCA,scale=TRUE,center=TRUE)
set.seed(rnd_seed)
tsn <- Rtsne(fPCA,perplexity=25)

pD.filtered$cc_tSNE1 <- tsn$Y[,1]
pD.filtered$cc_tSNE2 <- tsn$Y[,2]

tsnePlot <- ggplot(pD.filtered, aes(x=cc_tSNE1, y=cc_tSNE2, color=Condition, shape=Replicate)) +
    geom_point(alpha=0.8,size=2) +
    theme_bw()
tsnePlot
```

***
## Save Data
```{r}
pD.add <- select(pD.filtered, barcode, sf, tSNE1, tSNE2)
fD.add <- select(fD.filtered, id, highVar)
pD <- left_join(pD,pD.add, by="barcode")
fD <- left_join(fD,fD.add, by="id")
stopifnot(identical(as.character(pD$barcode),colnames(m)))
stopifnot(identical(as.character(fD$id),rownames(m)))
out <- list()
out[[1]] <- m
out[[2]] <- pD
out[[3]] <- fD
saveRDS(out,file="../data/Robjects/ExpressionList_QC.rds")
```
